crop

### 2023-05-09 scripts/crop2boundary.Rmd
names added

@@

```{r public land survey system only for west the front range}

bound_nm <- data.frame(
  y = c(31, 31, 50, 50, 31), 
  x = c(-105, -125, -125, -105, -103)
) %>% 
  st_as_sf(coords = c('x', 'y'), crs = 4326) %>% 
  st_bbox() %>% 
  st_as_sfc()

township <- st_read(
  '../geodata_raw/nationalPLSS/ilmocplss.gdb', layer = 'PLSSTownship', quiet = T
) %>% 
  st_cast('POLYGON') %>% 
  select(TWNSHPLAB)

bound_nm <- st_transform(bound_nm, st_crs(township))
township <- township[st_intersects(township, bound_nm) %>% lengths > 0, ]

section <- st_read(
  '../geodata_raw/nationalPLSS/ilmocplss.gdb', layer = 'PLSSFirstDivision', quiet = T
) %>% 
  st_cast('POLYGON') %>% 
  select(FRSTDIVLAB)

@@

trs <- st_join(township, section, .predicate = st_overlaps) %>% 
  mutate(TRS = paste0(TWNSHPLAB, ' S', FRSTDIVLAB)) %>% 
  select(TRS)

plot(trs)

before <- object.size(trs)
trs <- st_simplify(trs)
after <- object.size(trs)
after

@@

rm(section, township, trs)
```

>>>>

mason(dirin = '../geodata_raw/elevation/',
      dirout = '../geodata/elevation/',
      grid = tile_cellsV, fnames = 'cellname')

@@

```{r public land survey system only for land west of CO border, eval = F}

bound_nm <- data.frame(
  y = c(31, 31, 50, 50, 31), 
  x = c(-95, -125, -125, -95, -95)
) %>% 
  st_as_sf(coords = c('x', 'y'), crs = 4326) %>% 
  st_bbox() %>% 
  st_as_sfc()

township <- st_read(
  '../geodata_raw/nationalPLSS/ilmocplss.gdb', layer = 'PLSSTownship', quiet = T
) %>% 
  st_cast('POLYGON') %>% 
  select(TWNSHPLAB, PLSSID)

bound_nm <- st_transform(bound_nm, st_crs(township))
township <- township[st_intersects(township, bound_nm) %>% lengths > 0, ]
township <- st_drop_geometry(township)

section <- st_read(
  '../geodata_raw/nationalPLSS/ilmocplss.gdb', layer = 'PLSSFirstDivision', quiet = T
) %>% 
  st_cast('POLYGON') %>% 
  select(FRSTDIVLAB, PLSSID, FRSTDIVID)

@@

trs <- inner_join(section, township, 'PLSSID') %>% 
  mutate(TRS = paste(TWNSHPLAB, FRSTDIVLAB)) %>% 
  select(TRS)

before <- object.size(trs)
trs <- st_simplify(trs)
after <- object.size(trs)
object.size(trs)

@@

rm(section, township, trs, bound_nm, before, after)
```
